Density Matrix Susceptibility Tensors

### 2018-06-01 papers/1_dmatpol/paper-r1.tex
Table updated

% tables
%\usepackage{dcolumn}
\usepackage{multirow}
%\usepackage{hhline}
%\usepackage{booktabs}
%\usepackage{longtable}

@@

Performance descriptors of the \emph{ab initio} and generalized 
models of the density matrix susceptibility are shown in Table~\ref{t:results}. 
%
% Please add the following required packages to your document preamble:
\begin{table*}[]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
\textbf{}                                                                           &              & \textbf{An Initio} & \multicolumn{4}{c|}{\textbf{Generalized}}                     & \textbf{Multipole} \\ \hline
\textbf{Rank of DMS}                                                                & \textbf{Set} & \textbf{1, 0}      & \textbf{1, 0} & \textbf{2, 0} & \textbf{1, 1} & \textbf{2, 1} & \textbf{-}         \\ \hline
\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}RMSE\\ (kcal/mol)\end{tabular}}} & W            & 0.067 (99.80)      & 0.076 (99.74) & 0.053 (99.88) & 0.074 (99.76) & 0.050 (99.89) & 0.004 (100.00)     \\ \cline{2-8} 
                                                                                    & M            &                    &               &               &               &               &                    \\ \cline{2-8} 
                                                                                    & S            &                    &               &               &               &               &                    \\ \hline
\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}RMSD\\ (mD)\end{tabular}}}       & W            & 3.36 (98.70)       & 1.03 (99.88)  & 0.98 (99.89)  & 0.52 (99.97)  & 0.47 (99.98)  & 3.36 (98.70)       \\ \cline{2-8} 
                                                                                    & M            &                    &               &               &               &               &                    \\ \cline{2-8} 
                                                                                    & S            &                    &               &               &               &               &                    \\ \hline
\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}RMSQ\\ (DA10-3)\end{tabular}}}   & W            & 6.22 (58.72)       & 1.59 (97.32)  & 1.49 (97.62)  & 0.58 (99.64)  & 0.48 (99.75)  & 5.45 (68.30)       \\ \cline{2-8} 
                                                                                    & M            &                    &               &               &               &               &                    \\ \cline{2-8} 
                                                                                    & S            &                    &               &               &               &               &                    \\ \hline
\end{tabular}
\end{table*}
We considered three different types of point charge environment that generate
weak (0.001 -- 0.005 a.u.), 
moderate (0.001 -- 0.002 a.u.) and strong (0.002 -- 0.004 a.u.) 
electric fields around the water molecule (see the histograms of the electric field distribution
per atomic centre in Figure~XXX).
%
%for a set of varying point charge environments
%with weak, moderate and strong electric fields are shown in Table~XXX.

\begin{figure*}
\includegraphics[width=\textwidth]{data/dmatpol/water/figure1/fig-1.eps}
\caption{\label{f:results} {\bf Performance of the distributed density matrix susceptibility tensors in moderate
electric fields.}
Calculations of the electric field\hyp{}induced interaction energies (A-C), dipole moments (D-F) and
quadrupole moments (G-I).}
\end{figure*}

>>>>

% tables
%\usepackage{dcolumn}
\usepackage{multirow}
%\usepackage{hhline}
\usepackage{booktabs}
%\usepackage{longtable}

@@

Performance descriptors of the \emph{ab initio} and generalized 
models of the density matrix susceptibility are shown in Table~\ref{t:results}. 
%
\begin{table*}[]
\centering
\caption{My caption}
\label{t:results}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
\textbf{}                                                                           & \multicolumn{1}{l|}{} & \textbf{An Initio DMS} & \multicolumn{4}{c|}{\textbf{Generalized DMS}}                 & \textbf{Multipole} \\ \hline
\textbf{}                                                                           & \textbf{Set}          & \textbf{1, 0}          & \textbf{1, 0} & \textbf{2, 0} & \textbf{1, 1} & \textbf{2, 1} & \textbf{-}         \\ \hline
\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}RMSE\\ (kcal/mol)\end{tabular}}} & W                     & 0.067 (99.80)          & 0.076 (99.74) & 0.053 (99.88) & 0.074 (99.76) & 0.050 (99.89) & 0.004 (100.00)     \\ \cline{2-8} 
                                                                                    & M                     & 1.07 (96.96)           & 1.24 (95.96)  & 0.86 (98.06)  & 1.20 (96.17)  & 0.81 (98.27)  & 0.07 (99.99)       \\ \cline{2-8} 
                                                                                    & S                     & 4.22 (88.87)           & 5.15 (83.44)  & 3.60 (91.92)  & 5.02 (84.25)  & 3.41 (92.73)  & 0.33 (99.93)       \\ \hline
\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}RMSD\\ (mD)\end{tabular}}}       & W                     & 3.36 (98.70)           & 1.03 (99.88)  & 0.98 (99.89)  & 0.52 (99.97)  & 0.47 (99.98)  & 3.36 (98.70)       \\ \cline{2-8} 
                                                                                    & M                     & 14.72 (98.50)          & 7.72 (99.59)  & 6.86 (99.67)  & 6.15 (99.74)  & 5.38 (99.80)  & 14.72 (98.50)      \\ \cline{2-8} 
                                                                                    & S                     & 44.80 (96.92)          & 33.06 (98.32) & 29.49 (98.67) & 28.74 (98.73) & 26.25 (98.94) & 44.80 (96.92)      \\ \hline
\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}RMSQ\\ (DA10-3)\end{tabular}}}   & W                     & 6.22 (58.72)           & 1.59 (97.32)  & 1.49 (97.62)  & 0.58 (99.64)  & 0.48 (99.75)  & 5.45 (68.30)       \\ \cline{2-8} 
                                                                                    & M                     & 28.22 (53.90)          & 10.45 (93.68) & 8.83 (95.49)  & 8.25 (96.06)  & 6.57 (97.50)  & 23.94 (66.83)      \\ \cline{2-8} 
                                                                                    & S                     & 78.07 (40.53)          & 43.33 (81.68) & 35.73 (87.55) & 38.80 (85.31) & 31.59 (90.26) & 64.33 (59.62)      \\ \hline
\end{tabular}
\end{table*}
